Supplementary Material for the Paper ``Enriching Object Detection with\\ 2D-3D Registration and Continuous Viewpoint Estimation''

### 2015-04-01 2349.tex
rename files, add extended abstract template

\author{Christopher B. Choy, Michael Stark, Sam Corbett-Davies, Silvio Savarese\\
    Stanford University, Max Plank Institutes\\
    {\tt\small \{chrischoy, scorbett, stark, ssilvio\}@stanford.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}

@@

>>>>

\author{Christopher Bongsoo Choy\textsuperscript{\dag}, Michael Stark\textsuperscript{\dag \ddag}, Sam Corbett-Davies\textsuperscript{\dag}, Silvio Savarese\textsuperscript{\dag}\\
    Stanford University\textsuperscript{\dag}, Max Plank Institutes\textsuperscript{\ddag}\\
    {\tt\small \{chrischoy, scorbett, stark, ssilvio\}@stanford.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}

@@

\section{Acknowledgement}
This work has been supported by the Max Planck Center for Visual Computing \& Communication.

### 2015-04-01 egpaper_supp.tex
minor changes
rename files, add extended abstract template

%%%%%%%%% TITLE
\title{Supplementary Material for the Paper ``Enriching Object Detection with\\2D-3D Registration and Continuous Viewpoint Estimation''}
%\title{Enrich Object Detection : 2D-3D registration and continuous viewpoint estimation}

@@

We use $15\%$ context (extending the proposal region by $15\%$ on the
top, right, left, and bottom). We run our pipeline on the
PASCAL3D+~\cite{Xiang14} dataset, including our fine-tuning stage.
%
%If our method fails to estimate viewpoint (confidence score is below
%45), it
If our method fails to estimate viewpoint (confidence score is below a
threshold), it outputs 0 azimuth, 0 elevation, 0 yaw. Note that for
both categories and different numbers of viewpoints, our method has
difficulty distinguishing front and back views, but yields little
confusion between neighboring views. The failure cases given in
Fig.~\ref{fig:pascal3d_car_bad} and
Fig.~\ref{fig:pascal3d_bicycle_bad} are mostly caused by truncation,
occlusion, and unusual object shape.
%
\begin{figure*}[h]
  \centering
  \begin{tabular}{cc}
  \includegraphics[width=0.45\linewidth]{car_cnn4_crop.png}&
  \includegraphics[width=0.45\linewidth]{car_cnn8_crop.png}\\
    (a) Car, 4 views&
    (b) Car, 8 views\\
  \includegraphics[width=0.45\linewidth]{car_cnn16_crop.png}&
  \includegraphics[width=0.45\linewidth]{car_cnn24_crop.png}\\
    (c) Car, 16 views&
    (d) Car, 24 views\\
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn4_crop.png}&
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn8_crop.png}\\
    (e) Bicycle, 4 views&
    (j) Bicycle, 8 views\\  
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn16_crop.png}&
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn24_crop.png}\\
    (g) Bicycle, 16 views&
    (h) Bicycle, 24 views\\
  \end{tabular}
  \caption{Detection and pose estimation on PASCAL3D+~\cite{Xiang14}
    cars and bicycles.
    Average Precision (red) and Average Viewpoint Precision (green)
    are given in the left plot and viewpoint confusion table and MPPE
    are given in the right plot. The viewpoint index 1 is front, 2 is
    front-right, \dots, $n-1$ is front-left for number of viewpoints $n$.}
 % On the left, we
 %  present average precision curve (red) average viewpoint precision curve
 %  (green). On the right, we present confusion matrix and mean precision in pose
 %  estimation. Viewpoint index 1 is front, index 2 is front-right \dots and
 %  $n-1$ is front-left for number of viewpoints $n$.}
  \label{fig:pascal_ap}
\end{figure*}
%
\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
  \includegraphics[width=0.24\linewidth]{supp/occlusion1.png} &
  \includegraphics[width=0.24\linewidth]{supp/occlusion1b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car1a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car1b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car3a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car3b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car5a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car5b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car6a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car6b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car7a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car7b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car10a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car10b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car16a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car16b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car17a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car17b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car19a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car19b.png} \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car21a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car21b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car22a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car22b.png} \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car18a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car18b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car18c.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car18d.png} \\
  \hline
  \end{tabular}
  \caption{Successful detection and pose estimation results on
    PASCAL3D+~\cite{Xiang14} cars. Original image (left) and
  overlaid detection result (right). Proposal bounding box (blue) and
  predicted bounding box (purple).}
  \label{fig:pascal3d_car_good}
\end{figure*}

@@

\section{Fine Tuning}
Lastly, we provide qualitative examples of the fine-tuning stage of
our pipeline based on MCMC sampling (Sect.~5 in the main paper) in
Fig.~\ref{fig:tuning}. Please note that, while the visual difference
appear subtle, our method often manages to improve upon the initial
pose estimate.
%
\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{ccc}
  \includegraphics[width=0.22\linewidth]{supp/tuning_1a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_1b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_1c.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/tuning_2a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_2b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_2c.png}  \\ 
  \includegraphics[width=0.22\linewidth]{supp/tuning_3a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_3b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_3c.png}  \\   
  \includegraphics[width=0.22\linewidth]{supp/tuning_4a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_4b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_4c.png}  \\     
  \includegraphics[width=0.22\linewidth]{supp/tuning_5a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_5b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_5c.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/tuning_6a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_6b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_6c.png}  \\
  \end{tabular}
\caption{Effect of fine-tuning based on MCMC sampling. From left to
  right: original image, initial pose estimate, and fine-tuned
  result. Numbers indicate detection confidence (s) and intersection
  over union (o), respectively.} 
  \label{fig:tuning}
\end{figure*}

>>>>

%%%%%%%%% TITLE
\title{Supplementary Material for the Paper ``Enriching Object Detection with\\
2D-3D Registration and Continuous Viewpoint Estimation''}
%\title{Enrich Object Detection : 2D-3D registration and continuous viewpoint estimation}

@@

We use $15\%$ context (extending the proposal region by $15\%$ on the
top, right, left, and bottom). We run our pipeline on the
PASCAL3D+~\cite{Xiang14} dataset, including our fine-tuning stage.
%
%If our method fails to estimate viewpoint (confidence score is below
%45), it
If our method fails to estimate viewpoint (confidence score is below a
threshold), it outputs 0 azimuth, 0 elevation, 0 yaw. Note that for
both categories and different numbers of viewpoints, our method has
difficulty distinguishing front and back views, but yields little
confusion between neighboring views. The failure cases given in
Fig.~\ref{fig:pascal3d_car_bad} and
Fig.~\ref{fig:pascal3d_bicycle_bad} are mostly caused by truncation,
occlusion, and unusual object shape.
%
\begin{figure*}[h]
  \centering
  \begin{tabular}{cc}
  \includegraphics[width=0.45\linewidth]{car_cnn4_crop.png}&
  \includegraphics[width=0.45\linewidth]{car_cnn8_crop.png}\\
    (a) Car, 4 views&
    (b) Car, 8 views\\
  \includegraphics[width=0.45\linewidth]{car_cnn16_crop.png}&
  \includegraphics[width=0.45\linewidth]{car_cnn24_crop.png}\\
    (c) Car, 16 views&
    (d) Car, 24 views\\
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn4_crop.png}&
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn8_crop.png}\\
    (e) Bicycle, 4 views&
    (j) Bicycle, 8 views\\  
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn16_crop.png}&
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn24_crop.png}\\
    (g) Bicycle, 16 views&
    (h) Bicycle, 24 views\\
  \end{tabular}
  \caption{Detection and pose estimation on PASCAL3D+~\cite{Xiang14}
    cars and bicycles.
    Average Precision (red) and Average Viewpoint Precision (green)
    are given in the left plot and viewpoint confusion table and MPPE
    are given in the right plot. The viewpoint index 1 is front, 2 is
    front-right, \dots, $n-1$ is front-left for number of viewpoints $n$.}
 % On the left, we
 %  present average precision curve (red) average viewpoint precision curve
 %  (green). On the right, we present confusion matrix and mean precision in pose
 %  estimation. Viewpoint index 1 is front, index 2 is front-right \dots and
 %  $n-1$ is front-left for number of viewpoints $n$.}
  \label{fig:pascal_ap}
\end{figure*}
%
\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
  \includegraphics[width=0.24\linewidth]{supp/pas_aero1a.jpg} &
  \includegraphics[width=0.24\linewidth]{supp/pas_aero1b.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_aero2a.jpg} &
  \includegraphics[width=0.24\linewidth]{supp/pas_aero2b.png} \\
  \includegraphics[width=0.24\linewidth]{supp/pas_aero3a.jpg} &
  \includegraphics[width=0.24\linewidth]{supp/pas_aero3b.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_aero4a.jpg} &
  \includegraphics[width=0.24\linewidth]{supp/pas_aero4b.png} \\
  \hline
  \end{tabular}
  \caption{Successful detection and pose estimation results on
    PASCAL3D+~\cite{Xiang14} aeroplanes. Original image (left) and
  overlaid detection result (right). Proposal bounding box (blue) and
  predicted bounding box (purple).}
  \label{fig:pascal3d_aero_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
  \includegraphics[width=0.24\linewidth]{supp/occlusion1.png} &
  \includegraphics[width=0.24\linewidth]{supp/occlusion1b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car1a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car1b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car3a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car3b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car5a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car5b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car6a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car6b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car7a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car7b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car10a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car10b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car16a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car16b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car17a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car17b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car19a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car19b.png} \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car21a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car21b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car22a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car22b.png} \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car18a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car18b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car18c.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car18d.png} \\
  \hline
  \end{tabular}
  \caption{Successful detection and pose estimation results on
    PASCAL3D+~\cite{Xiang14} cars. Original image (left) and
  overlaid detection result (right). Proposal bounding box (blue) and
  predicted bounding box (purple).}
  \label{fig:pascal3d_car_good}
\end{figure*}

@@

\section{Fine Tuning}
Lastly, we provide qualitative examples of the fine-tuning stage of
our pipeline based on MCMC sampling (Sect.~5 in the main paper) in
Fig.~\ref{fig:tuning}. Please note that, while the visual difference
appear subtle, our method often manages to improve upon the initial
pose estimate.
%
\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{ccc}
  \includegraphics[width=0.22\linewidth]{supp/tuning_1a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_1b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_1c.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/tuning_7a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_7b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_7c.png}  \\ 
  \includegraphics[width=0.22\linewidth]{supp/tuning_3a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_3b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_3c.png}  \\   
  \includegraphics[width=0.22\linewidth]{supp/tuning_4a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_4b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_4c.png}  \\     
  \includegraphics[width=0.22\linewidth]{supp/tuning_5a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_5b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_5c.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/tuning_6a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_6b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_6c.png}  \\
  \end{tabular}
\caption{Effect of fine-tuning based on MCMC sampling. From left to
  right: original image, initial pose estimate, and fine-tuned
  result. Numbers indicate detection confidence (s) and intersection
  over union (o), respectively.} 
  \label{fig:tuning}
\end{figure*}
